---
title: "Review of Distributions"
author: "边蓓蕾"
date: "2019-06-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Properties of Distributions

- univariate/bivariate/multivariate distribution
- probability distributions
- probability density function $p(z)$

$P(z_{1}\leq z \leq z_{2})=\int_{z_{1}}^{z_{2}}p(x)dz$

### What is moment about the origin?

Moments. The moments of a distribution are a set of parameters that summarize it. Given a random variable $X$, its first moment about the origin, denoted , is defined to be $E[X]$. Its second moment about the origin is the population variance.

eg.

```{r}
# normal distribution
integrate(dnorm, -1.96, 1.96)
# negative exponential distribution
integrate(function(x) 2*exp(-2*x), 1/4, 1/2)
# expectation
integrate(function(x) x*2*exp(-2*x), 0, Inf)
```

#### normal distribution

$p(z)=(2\pi\sigma^2)^{-1/2}exp[-\frac{(z-\mu)^2}{2\sigma^2}]$

```{r}
curve(dnorm(x),
      xlim = c(-3.5, 3.5),
      ylab = "Density", 
      main = "Standard Normal Density Function")
```

#### central limit theorem

#### truncated normal distribution
plant and animal breeding, truncation selection
```{r}
library(truncnorm)
norm_data <- rnorm(n = 1000, mean = 90, sd = 4)
hist(norm_data)
truncnorm_data <- rtruncnorm(n = 1000, a = 85, b = 100, mean = 90, sd = 4)
mean(truncnorm_data)
sd(truncnorm_data)
hist(truncnorm_data)
```

#### confidence intervals